On particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2021-02-24 AvdMomZvolA_examples/ips_examples.tex
[AMZAE] Abstract

>>>>

\paragraph{Abstract.}
	A planar integral point set is a set of non-collinear points in plane
	such that for any pair of the  points the Euclidean distance
	between the points is integral.
	We discuss the classification of planar integral point sets
	and provide examples of sets that are not covered by the existent classification.
